Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-01-11 doc/reviews/ResponseToReviewer2.tex

\noindent
\comment{The abbreviation HAP is not defined in the text. I guess it stands for hydrophobic attraction potential.
}
\begin{itemize}
  \item Thank you for noticing this oversight. The definition of HAP has
    been added at its first occurrence in Section 3.1. 
\end{itemize}

@@

\noindent
\comment{$u$ is used for both the velocity and the solutions of the
Laplace equation. Please use another variable for the scalar function
$u$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$\rho$ used in the HAP is not the same as the one used in the
mobility boundary integral equation. One is a decay length of the
attraction potential, while the second is the Euclidean distance between
two JPs.}
\begin{itemize}
  \item We had used $\rho$ to denote the distance between source and
    target points in one of the layer potentials. This has been removed.

  \item We now use $\rho$ to denote the HAP decay length and $\rho_0$ to
    denote the cutoff for the repulsion force.
\end{itemize}

\noindent
\comment{$\nu$ is used on multiple instances, sometimes as a normal
vector (see line 97 for example), and other times as some scalar
function (see line 203).}
\begin{itemize}
  \item We now reserve $\boldsymbol{\nu}$ for the normal vector and
    $w_i$ denote the scalar what we previously defined to be $\nu_i$.
\end{itemize}

### 2022-01-11 doc/main_jfm.tex
reworked intro to section 4

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \cdot \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$. The Stokeslet and rotlets centred at $\aa_i$
are
\begin{align}
  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The Stokeslet is torque-free
and has force $\FF_i$ while the rotlet is force-free and has torque
$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
the limit of~\eqref{eq:velocity} with the rigid body motion, and
imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{align}
  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
\end{align}
denotes the jump of the limits of $g(\xx)$ taken from the outside to
the inside of $\Gamma_i$.
%\begin{align}
%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
%\lim_{\xx \to \xx_0^-}g(\xx), \quad
%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
%\end{align}
%denotes the limit taken from points in $U_i^c$,  the limit taken from
%points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{align}
  \label{eq:prejump}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
\end{align}
\end{lemma}
\begin{proof}
To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
\begin{align}
  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
\end{align}
By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
\setminus U_i$. Similarly, $w_i = u - u_i$ is smooth and $\nabla \cdot
{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
\begin{align}
  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
\end{align}
Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\begin{align}
  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = -\int_{\Gamma_i}  
    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
\end{align}
where the superscript denotes the limit taken from in $U_i$.  
Combining the above gives the first equation in \eqref{eq:prejump}.
The argument for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}

We have the following jump relations for \eqref{eq:uidef}: 
\begin{equation}
\label{eq:DLjump}
\jump{u_i} = \sigma, \quad
\jump{w_i} = 0, \quad
\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
\jump{\nabla w_i} = \mathbf{0},
\end{equation}
on $\Gamma_i$ (see, e.g. \cite{KlBaGrON13}). Therefore,
\begin{align*}
  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,w_i) \cdot \nnu +
    \SS(w_i,u_i) \cdot \nnu} \\
  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i w_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla w_i \mathbf{I} 
- 2\gamma\rho \nabla u_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
  u_i^T\right) \cdot \nnu \Big]\!\Big] \\
%  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
%- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
%  u_i^T\right) \cdot \nnu}\\
&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dw_i }{ds} \nnu
- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dw_i }{d\nnu} \ttau = \JJ_i.
\end{align*}
\todo[inline]{RR: Can you make sure the last line is correct? There was
an unbolded $\nu$ which I changed to a bolded $\nnu$.}
Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
as required.

@@

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles for
various particle shapes. In the present study, we fix the particle shape
and vary the background flows. Specifically, the particles are circular
disks with diameter $l_0 = 2.5$~nm. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle centre
and director respectively. The particle diameter is the thickness of
monolayers and the director points in the direction of the hydrophobic
side of the JP.

We use $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
nm}^{-1}$ for interfacial tension, and $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ for viscosity of room-temperature water. We
nondimensionalize the problem through the change of variables 
%\begin{equation}
%\label{eq:nondimensionalize}
$t \mapsto t \text{ ns}$,
$\xx \mapsto \xx \text{ nm}$, %\quad 
$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
$p \mapsto p \text{ pN nm}^{-2}$.
%\end{equation}
The numerical time step size is $\Delta t=0.2$.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Finally, we consider the parabolic background flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
$w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009} have shown that the behaviour of a vesicle in this
unbounded flow includes vertical migration, and depending on the flow
rate and reduced area, the steady-state shape can be either a symmetric
parachute or an asymmetric slipper.

>>>>

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{equation}
\label{eq:total_forces}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \cdot \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$. The Stokeslet and rotlets centred at $\aa_i$
are
\begin{align}
  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The Stokeslet is torque-free
and has force $\FF_i$ while the rotlet is force-free and has torque
$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
the limit of~\eqref{eq:velocity} with the rigid body motion, and
imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{align}
  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
\end{align}
denotes the jump of the limits of $g(\xx)$ taken from the outside to
the inside of $\Gamma_i$.
%\begin{align}
%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
%\lim_{\xx \to \xx_0^-}g(\xx), \quad
%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
%\end{align}
%denotes the limit taken from points in $U_i^c$,  the limit taken from
%points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{align}
  \label{eq:prejump}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
\end{align}
\end{lemma}
\begin{proof}
To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
\begin{align}
  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
\end{align}
By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
\setminus U_i$. Similarly, $w_i = u - u_i$ is smooth and $\nabla \cdot
{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
\begin{align}
  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
\end{align}
Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\begin{align}
  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
\end{align}
where the superscript denotes the limit taken from in $U_i$.  
Combining the above gives the first equation in \eqref{eq:prejump}.
The derivation for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}

We have the following jump relations for \eqref{eq:uidef}: 
\begin{equation}
\label{eq:DLjump}
\jump{u_i} = \sigma, \quad
\jump{w_i} = 0, \quad
\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
\jump{\nabla w_i} = \mathbf{0},
\end{equation}
on $\Gamma_i$ (see, e.g. \cite{KlBaGrON13}). Therefore,
\begin{align*}
  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,w_i) \cdot \nnu +
    \SS(w_i,u_i) \cdot \nnu} \\
  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i w_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla w_i \mathbf{I} 
- 2\gamma\rho \nabla u_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
  u_i^T\right) \cdot \nnu \Big]\!\Big] \\
%  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
%- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
%  u_i^T\right) \cdot \nnu}\\
&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dw_i }{ds} \nnu
- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dw_i }{d\nnu} \ttau = \JJ_i.
\end{align*}
%\todo[inline]{RR: Can you make sure the last line is correct? There was
%an unbolded $\nu$ which I changed to a bolded $\nnu$.} RJR -> Correct. Thank you.
Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
as required.

@@

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles. 
In the present work, we study JP vesicles in various background flows.
We also perform parametric studies of effective properties of the JP vesicles 
as a function of particle size and interaction strength.
An analysis of the relationship between particle shape on effective properties is beyond 
the scope of the current paper.

The particles are circular disks with centres 
$\aa_i$ and unit-length directors $\dd_i$ (Figure \ref{fig:figure0}(a)).
The simulations use the reference length $l_0 = 2.5$~nm representing the
thickness of a lipid monolayer.
The boundary conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$.
We nondimensionalize the PDE systems 
\eqref{eq:stokes}-\eqref{eq:total_forces}
problem through the change of variables 
%\begin{equation}
%\label{eq:nondimensionalize}
$t \mapsto t \text{ ns}$,
$\xx \mapsto \xx \text{ nm}$, %\quad 
$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
$p \mapsto p \text{ pN nm}^{-2}$.
%\end{equation}
The numerical time step size is $\Delta t=0.2$.

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
nm}^{-1}$ for interfacial tension.  The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water.

@@

For a single JP vesicle, we consider background flows for a shear flow 
(Section \ref{sec:ves_in_shear}), 
a parabolic flow (Section \ref{sec:ves_in_parabolic}),
and a quiescent flow (Section \ref{sec:ves_in_parabolic}). 
In addition to observing the familiar tank-treading motion, the shear
flow studies yield a friction coefficient for inter-monolayer slip 
and a critical rupture shear rate.  Permeability coefficients and 
stretching moduli arise from analyzing stretched JP vesicles in the 
quiescent background flow case.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
\label{sec:ves_in_parabolic}
Finally, we consider the parabolic background flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
$w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009} have shown that the behaviour of a vesicle in this
unbounded flow includes vertical migration, and depending on the flow
rate and reduced area, the steady-state shape can be either a symmetric
parachute or an asymmetric slipper.
